Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-06 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Typed a proof...

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\angle\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the latitude of $\ket{\psi}$. Conversely, $\angle^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\angle\left(\ket{\psi}\right)\in I}$.
For example, $\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
contains all states whose latitude is larger than $\theta_{0}$.\end{definition}

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$.\end{lemma}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{equation}
\begin{aligned}\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
\end{aligned}
\label{eq:includes}
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

Moreover, the same argument can apply on the great circle which is
not longitude. Since $\ket{\bar{1}}$ is the normal vector of the
gray circle which includes $\ket{2}$ and $\ket{\bar{2}}$, we have
$\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
are still the same.

Thus, we could plug $\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)=\left[l_{0},r_{0}\right]$
into equation~(\ref{eq:includes}), and get 
\begin{eqnarray*}
 &  & \left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\\
 & \Rightarrow & l_{0}+r_{0}=1
\end{eqnarray*}
Also, we have 
\begin{eqnarray*}
 &  & 1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\\
 & \Rightarrow & l_{0}\le\frac{1}{2}\le r_{0}
\end{eqnarray*}
Thus the lemma is proved.
\end{proof}
\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then $\theta_{0}>\frac{\pi}{4}$.\end{thm}
\begin{proof}
We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
we have $\left[\theta_{0},\frac{\pi}{2}\right]\cap\left[0,\frac{\pi}{2}-\theta_{0}\right]=\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\ne\emptyset$.
Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\right)$,
we have $\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$. Then, by lemma~\ref{lemma:imposs-imply-same-value},
for any $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{1}}\right)=\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$.
In another word, $\bar{f}$ maps every state to $\imposs$, and cannot
be an interval-valued frame function.
\end{proof}
\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then $\unknown\in\mathscr{I}$.\end{thm}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-2} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-2}This figure is used in
the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
of the yellow circle is $\theta_{0}=\frac{\pi}{2}-\frac{\pi}{5}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$,
and the latitude of the green circle is $\frac{\pi}{5}=\frac{\pi}{2}-\theta_{0}$.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
where the latitude of of the yellow circle is $\theta_{0}$ and the
latitude of of the green circle is $\frac{\pi}{2}-\theta_{0}$. Therefore,
$\bar{f}$ should map any state above the yellow circle to $\imposs$
and any states between the green circle and the equator to the same
interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$. 
\end{proof}

>>>>

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\angle\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the latitude of $\ket{\psi}$. Conversely, $\angle^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\angle\left(\ket{\psi}\right)\in I}$.
For example, the north pole has the latitude $0$, the equator has
the the latitude $\frac{\pi}{2}$, and $\angle^{-1}\left(\left[0,\theta_{0}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\angle\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
contains all states whose latitude is larger than $\theta_{0}$.\end{definition}

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$.\end{lemma}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{equation}
\begin{aligned}\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
\end{aligned}
\label{eq:includes}
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

Moreover, the same argument can apply on the great circle which is
not longitude. Since $\ket{\bar{1}}$ is the normal vector of the
gray circle which includes $\ket{2}$ and $\ket{\bar{2}}$, we have
$\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$,
even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
are still the same.

Thus, we could plug $\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)=\left[l_{0},r_{0}\right]$
into equation~(\ref{eq:includes}), and get 
\begin{eqnarray*}
 &  & \left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\\
 & \Rightarrow & l_{0}+r_{0}=1
\end{eqnarray*}
Also, we have 
\begin{eqnarray*}
 &  & 1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\\
 & \Rightarrow & l_{0}\le\frac{1}{2}\le r_{0}
\end{eqnarray*}
Thus the lemma is proved.
\end{proof}
\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then $\theta_{0}<\frac{\pi}{4}$.\end{thm}
\begin{proof}
We are going to prove by contradiction. Suppose $\theta_{0}\ge\frac{\pi}{4}$,
we have $\left[0,\theta_{0}\right]\cap\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]=\left[\frac{\pi}{2}-\theta_{0},\theta_{0}\right]\ne\emptyset$.
Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\theta_{0}\right]\right)$,
by lemma~\ref{lemma:imposs-imply-same-value}, we have $\imposs=\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]$,
where $l_{0}\in\left[0,\frac{\pi}{2}\right]$. A contradiction!
\end{proof}
\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left[\arcsin\left(\frac{1}{\sqrt{3}}\right),\frac{\pi}{4}\right)$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then $\unknown\in\mathscr{I}$.\end{thm}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-2} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-2}This figure is used in
the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
of the yellow circle is $\theta_{0}\in\left[\arcsin\left(\frac{1}{\sqrt{3}}\right),\frac{\pi}{4}\right)$,
and the latitude of the green circle is $\frac{\pi}{2}-\theta_{0}$.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
where the latitude of of the yellow circle is $\theta_{0}$ and the
latitude of of the green circle is $\frac{\pi}{2}-\theta_{0}$. Therefore,
$\bar{f}$ should map any state above the yellow circle to $\imposs$
and any states between the green circle and the equator to the same
interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$
by lemma~\ref{lemma:imposs-imply-same-value}.

When $\theta_{0}\ge\arcsin\left(\frac{1}{\sqrt{3}}\right)$, the latitude
of the green circle is $\theta_{0}\le\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$.
Now consider three states~$\ket{A}$, $\ket{B}$, and $\ket{C}$
whose latitude is $\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$
so that they are below the green circle, and these three states form
an equilateral triangle whose center is $H$. Since the latitude of
this triangle is $\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)$,
we know $\overline{OH}=\frac{1}{\sqrt{3}}$, where $O$ is the center
of the sphere. By the Pythagorean theorem, $\overline{HA}=\overline{HB}=\sqrt{\frac{2}{3}}$.
Notice that $\triangle HAB$ is an isosceles triangle with $\angle AHB=\frac{2\pi}{3}$,
we have $\overline{AB}=\sqrt{2}$. Since $\overline{OA}=\overline{OB}=1$
and $\overline{AB}=\sqrt{2}$, $\triangle OAB$ is an isosceles right
triangle with $\angle AHB=\frac{\pi}{2}$, i.e., $\ket{A}$ and $\ket{B}$
are orthogonal. Applying the same reason on all $\ket{A}$, $\ket{B}$,
and $\ket{C}$, $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an
orthonormal basis.

Since $\left\{ \ket{A},\ket{B},\ket{C}\right\} $ is an orthonormal
basis and $\bar{f}\left(\ket{A}\right)=\bar{f}\left(\ket{B}\right)=\bar{f}\left(\ket{C}\right)=\left[l_{0},1-l_{0}\right]$,
we have the following inequalities by lemma~\ref{lemma:interval-valued-frame-function}.
\begin{eqnarray*}
1\in\left[3l_{0},3-3l_{0}\right] & \Rightarrow & l_{0}\le\frac{1}{3}\\
\left[1,1\right]-\left[l_{0},1-l_{0}\right]\subseteq\left[2l_{0},2-2l_{0}\right] & \Rightarrow & l_{0}\le0
\end{eqnarray*}
Recall that $0\le l_{0}\le\frac{1}{2}$. Therefore, $l_{0}=0$, that
is, $\unknown=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$.
\end{proof}
